Use of asynchronous circuits and leakiness in modeling biological circuit of the Caulobacter Crescentus cell cycle

### 2017-02-16 asyncleakyn.tex
signal propagate

\section{Intro}
Biological modeling uses from stochastic to continuous to boolean models.  We propose an asynchronous circuit scheme for modeling the cell cycle of the bacteria Caulobacter Crescentus.   Asynchronous circuits are a type of digital circuits where the values are boolean, either 0 or 1, and the boolean functions are implemented through logic gates.  Digital circuits can be synchronous, where all of the logic gates in the circuit are controlled by some global clock, which ensures that the next values for all of the gates are updated at the same time.  Thus problems where various gate delays causing fluctuations in the circuit can be avoided.  In an asynchronous circuit, there is no global clock, and the gates update real time so different computational delay times for each gate cause real effects which may be propagated through the circuit.  Thus for an asynchronous circuit to provide reliable function, these random delays must be designed into the system.  A more stringent condition of asynchronous circuits known as speed independence ensures that no matter the delay for each gate, the circuit will function the same way. 
 different levels of detail

@@

The input and outputs of electronic devices similar to the chemical concentrations in a cell are actually continuous (analog).  The concept of a binary '1' or '0' is actually extracted from the original analog signal.  Thresholds allow the conversion of an analog signal into a binary signal.  Usually there is a low and a high threshold, and an in between region in which the signal is undetermined.(figure)  If the signal is below the low threshold then it is a binary '0' and if the signal is above the high threshold it is a binary '1'.  

@@

One basic property thresolds must satisfy is to allow proper propagation of the signal.  That is for the $i^{th}$ component which is connected to the $i+1^{th}$ component, $output_i low \leq input_{i+1} low$ and $output_i high \geq input_{i+1} high$.  In addition, if the signal is monotonic such as monotonically decreasing in the case of inverters then all inputs below the input low threshold or above the input high threshold gives valid output signals.  In multi input systems such as in biology where there can be multiple inputs to the same 'gate'.  In biological systems where the ODE model is a sigmomidal curve in the form of a Hill function, the partial derivative with respect to any one input variable is always monotonic.  Thus this satisfies our monotonic requirement and allow for proper propagation.  In addition, because these equations are monotonic with regard to any one variable, there are only a limited number of logic that can be formed.  (expand?)

>>>>

\section{Intro}
Biological modeling uses from stochastic to continuous to boolean models.  We propose an asynchronous circuit scheme for modeling the cell cycle of the bacteria Caulobacter Crescentus.   Asynchronous circuits are a type of digital circuits where the values are boolean, either 0 or 1, and the boolean functions are implemented through logic gates.  Digital circuits can be synchronous, where all of the logic gates in the circuit are controlled by some global clock, which ensures that the next values for all of the gates are updated at the same time.  Thus problems where various gate delays causing fluctuations in the circuit can be avoided.  In an asynchronous circuit, there is no global clock, and the gates update real time so different computational delay times for each gate cause real effects which may be propagated through the circuit.  Thus for an asynchronous circuit to provide reliable function, these random delays must be designed into the system.  A more stringent condition of asynchronous circuits known as speed independence ensures that no matter the delay for each gate, the circuit will function the same way. 
% different levels of detail

@@

The inputs and outputs of electronic devices are similar to the chemical concentrations in a cell which are all actually continuous values (analog).  The concept of a binary '1' or '0' is extracted from the original analog signal.  Thresholds allow the conversion of an analog signal into a binary signal.  Usually there is a low and a high threshold, and an in between region.(figure)  If the signal is below the low threshold then it is a binary '0' and if the signal is above the high threshold it is a binary '1'.  The in between region is undetermined meaning it is neither a '1' or a '0'.   

@@

One basic property thresolds must satisfy is to allow proper propagation of the signal.  The output of a gate should read as the same binary value into the input of the following gate.  That is for the $i^{th}$ component which is connected to the $i+1^{th}$ component, $output_i low \leq input_{i+1} low$ and $output_i high \geq input_{i+1} high$.  There is a naturally defined output threshold given the input thresholds.  That is passing the input threshold through the gate function G(). In addition, if the signal is monotonic then all inputs below the input low threshold or above the input high threshold gives valid output signals as well.  The reasoning is because for all $input low$ $x_i$ pairs, where $input low>x_i$ then $G(input low)>G(x_j)$ since G() is monotonic.  We also need to consider multiple input systems such as in biology where there can be multiple inputs to the same gate.  In biological systems where the ODE model is a sigmoidal curve in the form of a Hill function, the partial derivative with respect to any one input variable is always monotonic.  Thus this satisfies our monotonic requirement and allow for proper propagation.  In addition, because these equations are monotonic with regard to any one variable, there are only a limited number of logic that can be formed.  (expand?)
The other property that sigmoidal curves are important for is the restorative property of signals to allow for noise and increase robustness.  
